Income and Food Price Transmission\footnote{Revised version of ``Poverty and Price Transmission''. Submitted to \emph{Agricultural Economics} for review}

### 2016-01-29 tables.Rnw
Revised version. Note that the tp table created a failed message.

% !Rnw root = Master.Rnw

\SweaveInput{regressions.Rnw}

@@

<<echo=FALSE, results=tex>>=
library(stargazer)
sumdat = merge(infl, icp_data[,-5], by = "iso3c", all.x=TRUE)
sumdat = merge(sumdat, staples, by = "iso3c", all.x=TRUE)
sumdat = merge(sumdat, cdep, by = "iso3c", all.x=TRUE)
colnames(sumdat)=c("iso", "FPI inflation 07-08", "CPI inflation 07-08", "Real FPI growth 07-08", "FPI inflation 10-11", "CPI inflation 10-11", "Real FPI growth 10-11", "GDP", "cons", "food", "cshare", "cdep")

stargazer(sumdat, digits=1, title='Summary statistics', label = "tab:sumstat", 
          notes=c("Notes: 07-08 and 10-11 refer to the periods 2007:1-2008:6 and 2010:1-2010:12,", 
                  "respectively. `GDP, `cons' and `food' refer to per capita income, -consumption",
                  "and -food expenditure respectively in the year 2005. `cshare' refers to a coun-",
                  "try's percentage dietary energy supply derived from cereals, roots and tubers.", 
                  "`cdep' refers to a country's cereal import dependency ratio, both with respect",
                  "to the years 2004-06. Source: ILO, World Bank, FAO. Own calculations"),
          notes.append=FALSE,
          notes.align="l")
@

<<results=tex,echo=F>>=
<<dom_infl_0708>>
stargazer(m1, m2, m3, m4, m5, m6, title='Income related determinants of domestic food price changes 2007:1-2008:6', label = "tab:2007-8-regressions", dep.var.labels=c("FPI inflation","Real FPI growth"), no.space=TRUE, se = list(rse1, rse2, rse3, rse4, rse5, rse6), omit.stat = c("adj.rsq","f", "ser"), font.size = "footnotesize", covariate.labels=c("$log(GDP)$", "$log(GDP)^2$", "$log(cons)$", "$log(cons)^2$", "$log(food)$", "$log(food)^2$", "$cshare$", "$cdep$", "$cshare \\times cdep$"), 
          notes=c("Robust standard errors are reported in parentheses underneath the coefficients.",
                  "Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*', `**' and `***'", 
                  "respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<results=tex,echo=F>>=
<<dom_infl_1011>>
stargazer(m1, m2, m3, m4, m5, m6, title='Income related determinants of domestic food price changes 2010:1-2010:12', label = "tab:2010-11-regressions", dep.var.labels=c("FPI inflation","Real FPI growth"), no.space=TRUE, se = list(rse1, rse2, rse3, rse4, rse5, rse6), omit.stat = c("adj.rsq","f", "ser"), font.size = "footnotesize", covariate.labels=c("$log(GDP)$", "$log(GDP)^2$", "$log(cons)$", "$log(cons)^2$", "$log(food)$", "$log(food)^2$", "$cshare$", "$cdep$", "$cshare \\times cdep$"), 
          notes=c("Robust standard errors are reported in parentheses underneath the coefficients.",
                  "Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*', `**' and `***'", 
                  "respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<results=tex, echo=FALSE>>=
<<ts_pt>>
stargazer(m1, m2, m3, m4, m5, m6, title='Long run multiplier (LRM) regressions', label = "tab:lri-regressions", dep.var.labels=c("LRM, FPI inflation","LRM, real FPI growth"), no.space=TRUE, se = list(rse1, rse2, rse3, rse4, rse5, rse6), omit.stat = c("adj.rsq","f", "ser"), font.size = "footnotesize", covariate.labels=c("$log(GDP)$", "$log(GDP)^2$", "$log(cons)$", "$log(cons)^2$", "$log(food)$", "$log(food)^2$", "$cshare$", "$cdep$", "$cshare \\times cdep$"),
          notes=c("Robust standard errors are reported in parentheses underneath the coefficients.",
                  "Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*', `**' and `***'", 
                  "respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<results=tex, echo=FALSE>>=
<<panel_pt>>
stargazer(m1, m2, m3, m4, m5, m6, 
          title='Panel regressions', 
          label = "tab:panel-regressions", 
          font.size = "footnotesize", 
          no.space=TRUE, 
          se = list(rse1, rse2, rse3, rse4, rse5, rse6), 
          omit.stat = c("adj.rsq","f"), 
          dep.var.labels=c("$\\Delta log(FPI_{t})$","$\\Delta log(rFPI_{t})$"), 
          omit = 1:12, 
          covariate.labels=c("$\\Delta log(FAO_{t-6})$", "$\\Delta log(FAO_{t-6}) \\times log(GDP)$","$\\Delta log(FAO_{t-6}) \\times log(GDP)^2$", "$\\Delta log(FAO_{t-6}) \\times log(cons)$", "$\\Delta log(FAO_{t-6}) \\times log(cons)^2$", "$\\Delta log(FAO_{t-6}) \\times log(food)$", "$\\Delta log(FAO_{t-6}) \\times log(food)^2$"), 
          notes=c("Robust standard errors are reported in parentheses underneath the coef-",
                  "ficients. Significance at p = 0.1, p = 0.05 and p = 0.01 are denoted by `*',", 
                  " `**' and `***' respectively"),
          notes.append=FALSE,
          notes.align="l",
          notes.label="Notes:")
@

<<tpmat, echo=FALSE>>=
tp = matrix(NA, nrow=6, ncol=4)

<<dom_infl_0708>>
tp[1,1] = -m1$coefficients[2]/(2*m1$coefficients[3])
tp[2,1] = -m2$coefficients[2]/(2*m2$coefficients[3])
tp[3,1] = -m3$coefficients[2]/(2*m3$coefficients[3])
tp[4,1] = -m4$coefficients[2]/(2*m4$coefficients[3])
tp[5,1] = -m5$coefficients[2]/(2*m5$coefficients[3])
tp[6,1] = -m6$coefficients[2]/(2*m6$coefficients[3])

<<dom_infl_1011>>
tp[1,2] = -m1$coefficients[2]/(2*m1$coefficients[3])
tp[2,2] = -m2$coefficients[2]/(2*m2$coefficients[3])
tp[3,2] = -m3$coefficients[2]/(2*m3$coefficients[3])
tp[4,2] = -m4$coefficients[2]/(2*m4$coefficients[3])
tp[5,2] = -m5$coefficients[2]/(2*m5$coefficients[3])
tp[6,2] = -m6$coefficients[2]/(2*m6$coefficients[3])

<<ts_pt>>
tp[1,3] = -m1$coefficients[2]/(2*m1$coefficients[3])
tp[2,3] = -m2$coefficients[2]/(2*m2$coefficients[3])
tp[3,3] = -m3$coefficients[2]/(2*m3$coefficients[3])
tp[4,3] = -m4$coefficients[2]/(2*m4$coefficients[3])
tp[5,3] = -m5$coefficients[2]/(2*m5$coefficients[3])
tp[6,3] = -m6$coefficients[2]/(2*m6$coefficients[3])

<<panel_pt>>
tp[1,4] = -m1$coefficients[8]/(2*m1$coefficients[9])
tp[2,4] = -m2$coefficients[8]/(2*m2$coefficients[9])
tp[3,4] = -m3$coefficients[8]/(2*m3$coefficients[9])
tp[4,4] = -m4$coefficients[8]/(2*m4$coefficients[9])
tp[5,4] = -m5$coefficients[8]/(2*m5$coefficients[9])
tp[6,4] = -m6$coefficients[8]/(2*m6$coefficients[9])

tp = exp(tp)
@

@@

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}

@@

Model & dep. var & indep. var & tp (\$, PPP) & significance & \# of countries\tabularnewline

@@

(\ref{eq:infl_model}) & FPI infl. 07-08  & GDP & \Sexpr{round(tp[1,1],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[1,1] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])}  (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[1,1] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline

@@

(\ref{eq:infl_model}) & FPI infl. 07-08 & cons & \Sexpr{round(tp[2,1],0)} & no & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[2,1] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[2,1] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline

@@

(\ref{eq:infl_model}) & FPI infl. 07-08 & food & \Sexpr{round(tp[3,1],0)}  & yes & \Sexpr{nrow(data_0708[which(data_0708$food< tp[3,1] & data_0708$food >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$food>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$food< tp[3,1] & data_0708$food >0), ])/nrow(data_0708[which(data_0708$food>0), ])*100,0)}\%)\tabularnewline

@@

(\ref{eq:infl_model}) & rFPI gr. 07-08 & GDP & \Sexpr{round(tp[4,1],0)} & yes & \Sexpr{nrow(data_0708[which(data_0708$GDP< tp[4,1] & data_0708$GDP >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$GDP>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$GDP< tp[4,1] & data_0708$GDP >0), ])/nrow(data_0708[which(data_0708$GDP>0), ])*100,0)}\%)\tabularnewline

@@

(\ref{eq:infl_model}) & rFPI gr. 07-08 & cons & \Sexpr{round(tp[5,1],0)}  & yes & \Sexpr{nrow(data_0708[which(data_0708$cons< tp[5,1] & data_0708$cons >0), ])}/\Sexpr{nrow(data_0708[which(data_0708$cons>0), ])} (\Sexpr{round(nrow(data_0708[which(data_0708$cons< tp[5,1] & data_0708$cons >0), ])/nrow(data_0708[which(data_0708$cons>0), ])*100,0)}\%)\tabularnewline

@@

\multicolumn{6}{l}{Notes: The numbers in the fourth column refer to the estimated income or expenditure}\tabularnewline
\multicolumn{6}{l}{turning point (tp). The fifth column indicates whether the estimated quadratic term}\tabularnewline

>>>>

% !Rnw root = master1.Rnw

@@

\begin{table}[h]
\caption{Time series data on prices and exchange rates}
\label{tab:ts_data}
\begin{center}
{\small{}}%
\begin{tabular}{|c|>{\raggedright}m{5cm}|>{\raggedright}m{3cm}|>{\raggedright}p{3cm}|}
\hline 
\textbf{\small{}Variable} & \textbf{\small{}Description} & \textbf{\small{}Source} & \textbf{\small{}Expected effect}\tabularnewline
\hline 
{\small{}FPI} & {\small{}Domestic food price index.} & {\small{}ILO, LABORSTA} & -\tabularnewline
\hline
{\small{}CPI} & {\small{}Domestic consumer price index.} & {\small{}ILO, LABORSTA} & -\tabularnewline
\hline 
{\small{}Real FPI} & {\small{}Domestic real food price index. FPI deflated by the CPI} & {\small{}ILO, LABORSTA} & -\tabularnewline
\hline 
{\small{}FAO FPI} & {\small{}FAO food price index.} & {\small{}FAO} & Positive\tabularnewline
\hline 
{\small{}Real FAO FPI} & {\small{}Real FAO food price index. Nominal index deflated by the
World Bank Manufacturing Unit Value index} & {\small{}FAO} & Positive\tabularnewline
\hline 
{\small{}Exchange rate} & {\small{}Domestic currency/US\$ exchange rate} & {\small{}IMF} & Positive\tabularnewline
\hline 
\end{tabular}{\small \par}
\end{center}
\end {table}

\begin{table}[h]
\caption{Cross sectional data on country characteristics}
\label{tab:cs_data}
\begin{center}

{\small{}}%
\begin{tabular}{|c|>{\raggedright}m{5cm}|>{\raggedright}m{3cm}|>{\raggedright}p{3cm}|}
\hline 
\textbf{\small{}Variable} & \textbf{\small{}Description} & \textbf{\small{}Source} & \textbf{\small{}Expected effect}\tabularnewline
\hline 
{\small{}GDP} & {\small{}Gross domestic product. Log of per capita GDP (current int\$, PPP)} & {\small{}International Comparison Program 2005. World Bank database} & Inverse-U\tabularnewline
\hline 
{\small{}Consumption} & {\small{}Household consumption. Log of individual consumption expenditure by households (current int\$, PPP)} & {\small{}International Comparison Program 2005. World Bank database} & Inverse-U\tabularnewline
\hline 
{\small{}Cereal consumption share} & {\small{}Share of dietary energy supply derived from
cereals, roots and tubers (\%). 3-year average, 2004-06} & {\small{}FAO, FAOSTAT} & Positive\tabularnewline
\hline 
{\small{}Cereal import share} & {\small{}Cereal imports as a share of domestic supply (\%). 3-year average, 2004-06} & {\small{}FAO, FAOSTAT} & Positive\tabularnewline
\hline 
{\small{}Cereal export share} & {\small{}Cereal exports as a share of domestic production (\%). 3-year average, 2004-06} & {\small{}FAO, FAOSTAT} & Positive\tabularnewline
\hline 
{\small{}LLDC} & {\small{}Dummy. 1 if country is a landlocked developing country} & {\small{}UNCTAD} & Negative\tabularnewline
\hline 
{\small{}Trade openness} & {\small{}Sum of exports and imports of goods and services as a share of GDP (\%). 2006-10 average} & {\small{}World Bank Development Indicators} & Positive\tabularnewline
\hline 
{\small{}DTF} & {\small{}Distance to Frontier index. An economy\textquoteright s distance to frontier measured on a scale from 0 to 100, where 0 represents the lowest performance and 100 the frontier.} & {\small{}Doing Business survey, Trading Across Borders . World Bank} & Positive\tabularnewline
\hline 
{\small{}LPI} & {\small{} Logistics performance index. The LPI measures ease of trade and transport of goods. The index ranges from 1 to 5, with a higher score representing better performance.} & {\small{}Logistics Performance Index 2007. World Bank database} & Positive\tabularnewline
\hline 
\end{tabular}{\small \par}
\end{center}
\end {table}

<<results=tex,echo=F>>=
library(stargazer)
reg.list = readRDS("fpi_reg_m.rds")
se.list = readRDS("fpi_reg_se.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of domestic FPI inflation 2007-8 and 2010-11', 
          label = "tab:fpi-regressions", 
          dep.var.labels=c("FPI inflation 07-08", "FPI inflation 10-11"), 
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize", 
          covariate.labels=c("log of GDP",
                             "log of GDP squared", 
                             "log of consumption", 
                             "log of consumption squared", 
                             "Cereal consumption share", 
                             "Cereal import share", 
                             "Cereal export share",
                             "LLDC",
                             "State trading enterprice",
                             "Trade openness", 
                             "DTF", 
                             "LPI"))
@

<<results=tex,echo=F>>=
reg.list = readRDS("rfpi_reg_m.rds")
se.list = readRDS("rfpi_reg_se.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of domestic real FPI growth 2007-8 and 2010-11', 
          label = "tab:rfpi-regressions", 
          dep.var.labels=c("Real FPI growth 07-08", "Real FPI growth 10-11"), 
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize", 
          covariate.labels=c("log of GDP",
                             "log of GDP squared", 
                             "log of consumption", 
                             "log of consumption squared", 
                             "Cereal consumption share", 
                             "Cereal import share", 
                             "Cereal export share",
                             "LLDC",
                             "State trading enterprice", 
                             "Trade openness", 
                             "DTF", 
                             "LPI"))
@

<<results=tex,echo=F>>=
reg.list = readRDS("int_reg_m.rds")
se.list = readRDS("int_reg_se.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of domestic FPI inflation 2007-8', 
          label = "tab:int-regressions", 
          dep.var.labels=c("FPI inflation 07-08", "Real FPI growth 07-08"), 
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize", 
          covariate.labels=c("log of GDP",
                             "log of GDP squared", 
                             "log of consumption", 
                             "log of consumption squared", 
                             "Cereal consumption share", 
                             "Cereal import share", 
                             "Cereal export share",
                             "LLDC", 
                             "State trading enterprice",
                             "Trade openness", 
                             "DTF", 
                             "LPI",
                             "Export restrictions",
                             "Price controls",
                             "Stock releases",
                             "Tariff reductions",
                             "Tax reductions"))
@

<<results=tex,echo=F>>=
library(stargazer)
reg.list = readRDS("fpi_pt_reg_m.rds")
se.list = readRDS("fpi_pt_reg_se.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of long run FPI transmission rates', 
          label = "tab:fpi-pt-regressions", 
          dep.var.labels=c("FPI transmission LRM"), 
          column.labels = c("OLS", "WLS"),
          column.separate = c(2, 2),
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize", 
          covariate.labels=c("log of GDP",
                             "log of GDP squared", 
                             "log of consumption", 
                             "log of consumption squared",
                             "Cereal consumption share", 
                             "Cereal import share", 
                             "Cereal export share",
                             "LLDC", 
                             "Trade openness", 
                             "DTF", 
                             "LPI"))
@

<<results=tex,echo=F>>=
reg.list = readRDS("rfpi_pt_reg_m.rds")
se.list = readRDS("rfpi_pt_reg_se.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Determinants of long run real FPI transmission rates', 
          label = "tab:rfpi-pt-regressions", 
          dep.var.labels=c("Real FPI transmission LRM"), 
          column.labels = c("OLS", "WLS"),
          column.separate = c(2, 2),
          no.space=TRUE,
          se = list(se.list[[1]], se.list[[2]], se.list[[3]], se.list[[4]]), 
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize", 
          covariate.labels=c("log of GDP",
                             "log of GDP squared", 
                             "log of consumption", 
                             "log of consumption squared",
                             "Cereal consumption share", 
                             "Cereal import share", 
                             "Cereal export share",
                             "LLDC", 
                             "Trade openness", 
                             "DTF", 
                             "LPI"))
@

<<results=tex, echo=FALSE>>=
library(plm)
reg.list = readRDS("panel_reg_m.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Dynamic panel regressions (within (FE) estimator)', 
          label = "tab:fe-panel-regressions", 
          dep.var.labels=c("FPI inflation", "Real FPI growth"), 
          no.space=TRUE,
          omit = c("adj.fpi", "rfpi"),
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize",
          covariate.labels=c("$\\pi_{t}^{i}$",
                             "$\\pi_{t-1}^{i}$",
                             "$\\Delta \\log(er_{t})$",
                             "$\\Delta \\log(er_{t-1})$",
                             "$\\pi_{t}^{i}\\times \\text{log of GDP}$",
                             "$\\pi_{t}^{i}\\times \\text{log of GDP squared}$", 
                             "$\\pi_{t}^{i}\\times \\text{log of consumption}$", 
                             "$\\pi_{t}^{i}\\times \\text{log of consumption squared}$", 
                             "$\\pi_{t}^{i}\\times \\text{Cereal consumption share}$", 
                             "$\\pi_{t}^{i}\\times \\text{Cereal import share}$", 
                             "$\\pi_{t}^{i}\\times \\text{Cereal export share}$",
                             "$\\pi_{t}^{i}\\times \\text{LLDC}$", 
                             "$\\pi_{t}^{i}\\times \\text{Trade openness}$", 
                             "$\\pi_{t}^{i}\\times \\text{DTF}$", 
                             "$\\pi_{t}^{i}\\times \\text{LPI}$"))
@

<<results=tex, echo=FALSE>>=
library(plm)
reg.list = readRDS("panel_reg_fd_m.rds")

stargazer(reg.list[[1]], reg.list[[2]], reg.list[[3]], reg.list[[4]],
          title='Dynamic panel regressions (Anderson-Hsiao (AH) estimator)', 
          label = "tab:fd-panel-regressions", 
          dep.var.labels=c("FPI inflation", "Real FPI growth"), 
          no.space=TRUE,
          omit = c("adj.fpi", "rfpi"),
          omit.stat = c("adj.rsq","f", "ser"), 
          font.size = "footnotesize",
          covariate.labels=c("$\\pi_{t}^{i}$",
                             "$\\pi_{t-1}^{i}$",
                             "$\\Delta \\log(er_{t})$",
                             "$\\Delta \\log(er_{t-1})$",
                             "$\\pi_{t}^{i}\\times \\text{log of GDP}$",
                             "$\\pi_{t}^{i}\\times \\text{log of GDP squared}$", 
                             "$\\pi_{t}^{i}\\times \\text{log of consumption}$", 
                             "$\\pi_{t}^{i}\\times \\text{log of consumption squared}$", 
                             "$\\pi_{t}^{i}\\times \\text{Cereal consumption share}$", 
                             "$\\pi_{t}^{i}\\times \\text{Cereal import share}$", 
                             "$\\pi_{t}^{i}\\times \\text{Cereal export share}$",
                             "$\\pi_{t}^{i}\\times \\text{LLDC}$", 
                             "$\\pi_{t}^{i}\\times \\text{Trade openness}$", 
                             "$\\pi_{t}^{i}\\times \\text{DTF}$", 
                             "$\\pi_{t}^{i}\\times \\text{LPI}$"))
@

<<echo=FALSE>>=

## Remember to change variable names!!!!!

load("ctr_dat_0708.Rda")
dat = ctr.dat.0708
r1 = readRDS("fpi_reg_m.rds")
r2 = readRDS("rfpi_reg_m.rds")
r3 = readRDS("int_reg_m.rds")
r4 = readRDS("fpi_pt_reg_m.rds")
r5 = readRDS("rfpi_pt_reg_m.rds")
r6 = readRDS("panel_reg_m.rds")
r7 = readRDS("panel_reg_fd_m.rds")

tp = matrix(NA, nrow=4, ncol=7)

tp[1,1] = -coef(r1[[1]])["log(gdp)"]/(2*coef(r1[[1]])["I(log(gdp)^2)"])
tp[2,1] = -coef(r1[[2]])["log(cons)"]/(2*coef(r1[[2]])["I(log(cons)^2)"])
tp[3,1] = -coef(r1[[3]])["log(gdp)"]/(2*coef(r1[[3]])["I(log(gdp)^2)"])
tp[4,1] = -coef(r1[[4]])["log(cons)"]/(2*coef(r1[[4]])["I(log(cons)^2)"])

tp[1,2] = -coef(r2[[1]])["log(gdp)"]/(2*coef(r2[[1]])["I(log(gdp)^2)"])
tp[2,2] = -coef(r2[[2]])["log(cons)"]/(2*coef(r2[[2]])["I(log(cons)^2)"])
tp[3,2] = -coef(r2[[3]])["log(gdp)"]/(2*coef(r2[[3]])["I(log(gdp)^2)"])
tp[4,2] = -coef(r2[[4]])["log(cons)"]/(2*coef(r2[[4]])["I(log(cons)^2)"])

tp[1,3] = -coef(r3[[1]])["log(gdp)"]/(2*coef(r3[[1]])["I(log(gdp)^2)"])
tp[2,3] = -coef(r3[[2]])["log(cons)"]/(2*coef(r3[[2]])["I(log(cons)^2)"])
tp[3,3] = -coef(r3[[3]])["log(gdp)"]/(2*coef(r3[[3]])["I(log(gdp)^2)"])
tp[4,3] = -coef(r3[[4]])["log(cons)"]/(2*coef(r3[[4]])["I(log(cons)^2)"])

tp[1,4] = -coef(r4[[1]])["log(gdp)"]/(2*coef(r4[[1]])["I(log(gdp)^2)"])
tp[2,4] = -coef(r4[[2]])["log(cons)"]/(2*coef(r4[[2]])["I(log(cons)^2)"])
tp[3,4] = -coef(r4[[3]])["log(gdp)"]/(2*coef(r4[[3]])["I(log(gdp)^2)"])
tp[4,4] = -coef(r4[[4]])["log(cons)"]/(2*coef(r4[[4]])["I(log(cons)^2)"])

tp[1,5] = -coef(r5[[1]])["log(gdp)"]/(2*coef(r5[[1]])["I(log(gdp)^2)"])
tp[2,5] = -coef(r5[[2]])["log(cons)"]/(2*coef(r5[[2]])["I(log(cons)^2)"])
tp[3,5] = -coef(r5[[3]])["log(gdp)"]/(2*coef(r5[[3]])["I(log(gdp)^2)"])
tp[4,5] = -coef(r5[[4]])["log(cons)"]/(2*coef(r5[[4]])["I(log(cons)^2)"])

tp[1,6] = -coef(r6[[1]])["I(lag(diff(log(fao.fpi)), 0) * log(gdp))"]/
  (2*coef(r6[[1]])["I(lag(diff(log(fao.fpi)), 0) * I(log(gdp)^2))"])
tp[2,6] = -coef(r6[[2]])["I(lag(diff(log(fao.fpi)), 0) * log(cons))"]/
  (2*coef(r6[[2]])["I(lag(diff(log(fao.fpi)), 0) * I(log(cons)^2))"])
tp[3,6] = -coef(r6[[3]])["I(lag(diff(log(fao.fpi)), 0) * log(gdp))"]/
  (2*coef(r6[[3]])["I(lag(diff(log(fao.fpi)), 0) * I(log(gdp)^2))"])
tp[4,6] = -coef(r6[[4]])["I(lag(diff(log(fao.fpi)), 0) * log(cons))"]/
  (2*coef(r6[[4]])["I(lag(diff(log(fao.fpi)), 0) * I(log(cons)^2))"])

tp[1,7] = -coef(r7[[1]])["I(lag(log(fao.fpi), 0) * log(gdp))"]/
  (2*coef(r7[[1]])["I(lag(log(fao.fpi), 0) * I(log(gdp)^2))"])
tp[2,7] = -coef(r7[[2]])["I(lag(log(fao.fpi), 0) * log(cons))"]/
  (2*coef(r7[[2]])["I(lag(log(fao.fpi), 0) * I(log(cons)^2))"])
tp[3,7] = -coef(r7[[3]])["I(lag(log(fao.fpi), 0) * log(gdp))"]/
  (2*coef(r7[[3]])["I(lag(log(fao.fpi), 0) * I(log(gdp)^2))"])
tp[4,7] = -coef(r7[[4]])["I(lag(log(fao.fpi), 0) * log(cons))"]/
  (2*coef(r7[[4]])["I(lag(log(fao.fpi), 0) * I(log(cons)^2))"])

tp = exp(tp)

nc = matrix(NA, nrow=4, ncol=7)
nc.pc = matrix(NA, nrow=4, ncol=7)
n.gdp = nrow(dat[which(dat$gdp>0), ])
n.cons = nrow(dat[which(dat$cons>0), ])

nc[1,1] = nrow(dat[which(dat$gdp< tp[1,1] & dat$gdp >0), ])
nc[2,1] = nrow(dat[which(dat$cons< tp[2,1] & dat$cons >0), ])
nc[3,1] = nrow(dat[which(dat$gdp< tp[3,1] & dat$gdp >0), ])
nc[4,1] = nrow(dat[which(dat$cons< tp[4,1] & dat$cons >0), ])

nc.pc[1,1] = round(nc[1,1]/n.gdp*100,0)
nc.pc[2,1] = round(nc[2,1]/n.cons*100,0)
nc.pc[3,1] = round(nc[3,1]/n.gdp*100,0)
nc.pc[4,1] = round(nc[4,1]/n.cons*100,0)

nc[1,2] = nrow(dat[which(dat$gdp< tp[1,2] & dat$gdp >0), ])
nc[2,2] = nrow(dat[which(dat$cons< tp[2,2] & dat$cons >0), ])
nc[3,2] = nrow(dat[which(dat$gdp< tp[3,2] & dat$gdp >0), ])
nc[4,2] = nrow(dat[which(dat$cons< tp[4,2] & dat$cons >0), ])

nc.pc[1,2] = round(nc[1,2]/n.gdp*100,0)
nc.pc[2,2] = round(nc[2,2]/n.cons*100,0)
nc.pc[3,2] = round(nc[3,2]/n.gdp*100,0)
nc.pc[4,2] = round(nc[4,2]/n.cons*100,0)

nc[1,3] = nrow(dat[which(dat$gdp< tp[1,3] & dat$gdp >0), ])
nc[2,3] = nrow(dat[which(dat$cons< tp[2,3] & dat$cons >0), ])
nc[3,3] = nrow(dat[which(dat$gdp< tp[3,3] & dat$gdp >0), ])
nc[4,3] = nrow(dat[which(dat$cons< tp[4,3] & dat$cons >0), ])

nc.pc[1,3] = round(nc[1,3]/n.gdp*100,0)
nc.pc[2,3] = round(nc[2,3]/n.cons*100,0)
nc.pc[3,3] = round(nc[3,3]/n.gdp*100,0)
nc.pc[4,3] = round(nc[4,3]/n.cons*100,0)

nc[1,4] = nrow(dat[which(dat$gdp< tp[1,4] & dat$gdp >0), ])
nc[2,4] = nrow(dat[which(dat$cons< tp[2,4] & dat$cons >0), ])
nc[3,4] = nrow(dat[which(dat$gdp< tp[3,4] & dat$gdp >0), ])
nc[4,4] = nrow(dat[which(dat$cons< tp[4,4] & dat$cons >0), ])

nc.pc[1,4] = round(nc[1,4]/n.gdp*100,0)
nc.pc[2,4] = round(nc[2,4]/n.cons*100,0)
nc.pc[3,4] = round(nc[3,4]/n.gdp*100,0)
nc.pc[4,4] = round(nc[4,4]/n.cons*100,0)

nc[1,5] = nrow(dat[which(dat$gdp< tp[1,5] & dat$gdp >0), ])
nc[2,5] = nrow(dat[which(dat$cons< tp[2,5] & dat$cons >0), ])
nc[3,5] = nrow(dat[which(dat$gdp< tp[3,5] & dat$gdp >0), ])
nc[4,5] = nrow(dat[which(dat$cons< tp[4,5] & dat$cons >0), ])

nc.pc[1,5] = round(nc[1,5]/n.gdp*100,0)
nc.pc[2,5] = round(nc[2,5]/n.cons*100,0)
nc.pc[3,5] = round(nc[3,5]/n.gdp*100,0)
nc.pc[4,5] = round(nc[4,5]/n.cons*100,0)

nc[1,6] = nrow(dat[which(dat$gdp< tp[1,6] & dat$gdp >0), ])
nc[2,6] = nrow(dat[which(dat$cons< tp[2,6] & dat$cons >0), ])
nc[3,6] = nrow(dat[which(dat$gdp< tp[3,6] & dat$gdp >0), ])
nc[4,6] = nrow(dat[which(dat$cons< tp[4,6] & dat$cons >0), ])

nc.pc[1,6] = round(nc[1,6]/n.gdp*100,0)
nc.pc[2,6] = round(nc[2,6]/n.cons*100,0)
nc.pc[3,6] = round(nc[3,6]/n.gdp*100,0)
nc.pc[4,6] = round(nc[4,6]/n.cons*100,0)

nc[1,7] = nrow(dat[which(dat$gdp< tp[1,7] & dat$gdp >0), ])
nc[2,7] = nrow(dat[which(dat$cons< tp[2,7] & dat$cons >0), ])
nc[3,7] = nrow(dat[which(dat$gdp< tp[3,7] & dat$gdp >0), ])
nc[4,7] = nrow(dat[which(dat$cons< tp[4,7] & dat$cons >0), ])

nc.pc[1,7] = round(nc[1,7]/n.gdp*100,0)
nc.pc[2,7] = round(nc[2,7]/n.cons*100,0)
nc.pc[3,7] = round(nc[3,7]/n.gdp*100,0)
nc.pc[4,7] = round(nc[4,7]/n.cons*100,0)

nc.pc.colmean = colMeans(nc.pc)
nc.pc.mean = mean(nc.pc.colmean)
nc.pc.panel.mean = mean(nc.pc.colmean[6:7])
nc.pc.nonpanel.mean = mean(nc.pc.colmean[-(6:7)])
@

@@

\small
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}

@@

Table & Estimator & dep. var & indep. var & tp (\$, PPP) & sign. & \# ctrs left of tp.\tabularnewline

@@

\ref{tab:fpi-regressions} & OLS & FPI infl. 07-08  & GDP & \Sexpr{round(tp[1,1],0)} & yes & \Sexpr{nc[1,1]}/\Sexpr{n.gdp} (\Sexpr{nc.pc[1,1]} \%) \tabularnewline

@@

\ref{tab:fpi-regressions} & OLS & FPI infl. 07-08  & Cons & \Sexpr{round(tp[2,1],0)} & yes & \Sexpr{nc[2,1]}/\Sexpr{n.cons} (\Sexpr{nc.pc[2,1]} \%) \tabularnewline

@@

\ref{tab:fpi-regressions} & OLS & FPI infl. 10-11  & GDP & \Sexpr{round(tp[3,1],0)} & no & \Sexpr{nc[3,1]}/\Sexpr{n.gdp} (\Sexpr{nc.pc[3,1]} \%) \tabularnewline

@@

\ref{tab:fpi-regressions} & OLS & FPI infl. 10-11  & Cons & \Sexpr{round(tp[4,1],0)} & yes & \Sexpr{nc[4,1]}/\Sexpr{n.cons} (\Sexpr{nc.pc[4,1]} \%) \tabularnewline

@@

\ref{tab:rfpi-regressions} & OLS & rFPI growth 07-08  & GDP & \Sexpr{round(tp[1,2],0)} & yes & \Sexpr{nc[1,2]}/\Sexpr{n.gdp} (\Sexpr{nc.pc[1,2]} \%) \tabularnewline

@@

\ref{tab:fd-panel-regressions} & AH & FPI infl.  & GDP & \Sexpr{round(tp[1,7],0)} & no & \Sexpr{nc[1,7]}/\Sexpr{n.gdp} (\Sexpr{nc.pc[1,7]} \%) \tabularnewline
